---
title: "doctest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{doctest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the vignette for the \'doctest\' package. 
The \'doctest\' package was build for the Coursera cours \'buidling R package\'.
It includes accident data form the years 2013, 2014, 2015 and may be used 
to create summary statistics and plots of the US accident data. 

The user-level functions are `fars_summarize_years` and `fars_map_state` which 
we will demonstrate below. See the help files for function-specific help. 

Please note that the functions were slightly adapted as compared to the original 
versions from the Coursera course. 
This was mainly because I preferred to have the datasets within thew package itself
instead of relying having the data in an appropriate folder structure outside of 
the package.

## Load the package
Once the package is downloaded from Github and installed it may be loaded by
```{r instl, eval = FALSE}
library('devtools')
devtools::install_github("time-to-MaBo/doctest")
```

```{r setup}
library(doctest)
?doctest
help(package = "doctest")
```

## `fars_summarize_years`
The function gives counts of accidents by year and month.

```{r summary}
fars_summarize_years(2013:2015)
```

## `fars_summarize_years`
The function plots the location of the accidents within a chosen state and year

```{r state}
fars_map_state(1,2013)
```


